\bf Title

### 2024-01-17 article/paper_padic_spec.tex
commit by Simone

We recall that that the smallest affine space of $K^n$ containing a set $P \subset K^n$ is called its
\emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and defines the affine hull of $P$. The \emph{dimension}
of $P$ is defined as $n-e$ (namely the dimension of its affine hull).

@@

That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}. This problem is the optimization problem: 
\begin{equation}
  \tag{dLP}\label{dLP}
\begin{array}{rcll}
  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.

>>>>

We recall that that the smallest affine space of $K^n$ containing a set $P \subset K^n$ is called its
\emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and since the forms $m_i$ are affinely independent, it
defines the affine hull of $P$. The \emph{dimension} of $P$ is defined as $n-e$ (namely the dimension of
its affine hull).

@@

That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}. This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
\begin{equation}
  \tag{dLP}\label{dLP}
\begin{array}{rcll}
  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.
